---
title: "Country Aggregates"
author: "Mark Wheldon"
date: |
    | `r Sys.Date()`
    | (`r paste0("_FPEMglobal_ version ", packageVersion("FPEMglobal"), ")")`
output:
    function(...) rmarkdown::html_vignette(..., css=c(system.file("rmarkdown", "templates", "html_vignette", "resources", "vignette.css", package = "rmarkdown"), "vignette2.css")):
      toc: true
bibliography: bibliography.bib
csl: 'apa-single-spaced.csl'
link-citations: true
vignette: >
  %\VignetteIndexEntry{Country Aggregates}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = FALSE
)

 ## set global chunk options
options(formatR.arrow=TRUE,width=80)
```

```{r setup}
library(FPEMglobal)
```

<!-- 
STYLE CONVENTIONS
- Filenames: single quoted
- Software: italics
-->


---

You can access this vignette from the *R* console by typing `vignette("country_aggregates", package = "FPEMglobal")`.

---


# Introduction

*FPEMglobal* produces estimates and projections of family planning indicators for both countries and areas and their aggregations. There are several sets of aggregates, with most based on geography (e.g., geographic regions), development indicators (e.g., "least developed countries", "small island developing states"), or historical statistical classifications (e.g., "developing regions", @UN_M49). This vignette lists and compares the aggregates included in the *FPEMglobal* package. 





# References {-}
