---
title: "Development Notes"
author: "Mark Wheldon"
date: |
    | `r Sys.Date()`
    | (`r paste0("_FPEMglobal_ version ", packageVersion("FPEMglobal"), ")")`
output:
    function(...) rmarkdown::html_vignette(..., css=c(system.file("rmarkdown", "templates", "html_vignette", "resources", "vignette.css", package = "rmarkdown"), "vignette2.css")):
      toc: true
bibliography: bibliography.bib
csl: 'apa-single-spaced.csl'
link-citations: true
vignette: >
  %\VignetteIndexEntry{Country Aggregates}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = FALSE
)

 ## set global chunk options
options(formatR.arrow=TRUE,width=80)
```

```{r setup}
library(FPEMglobal)
```

<!-- 
STYLE CONVENTIONS
- Filenames: single quoted
- Software: italics
-->


---

You can access this vignette from the *R* console by typing `vignette("development_notes", package = "FPEMglobal")`.

---


# Description

This document contains detailed descriptions of changes made over successive revisions of the package that are too long or arcane for the NEWS file. It is intended mainly for use by package developers to keep a record of these revisions. 







# References {-}
