---
title: "Family Planning Estimation Model for Adolescent Women Aged 15--19"
author: "Mark Wheldon"
date: |
    | `r Sys.Date()`
    | (`r paste0("_FPEMglobal_ version ", packageVersion("FPEMglobal"), ")")`
output:
    function(...) rmarkdown::html_vignette(..., css=c(system.file("rmarkdown", "templates", "html_vignette", "resources", "vignette.css", package = "rmarkdown"), "vignette2.css")):
      toc: true
bibliography: bibliography.bib
link-citations: true
vignette: >
  %\VignetteIndexEntry{Family Planning Estimation Model for Adolescent Women Aged 15--19}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

## set global chunk options
options(formatR.arrow=TRUE,width=80)
```

<!-- 
STYLE CONVENTIONS
- Filenames: single quoted
- Software: italics
-->

You can access this vignette from the *R* console by typing `vignette("FPEMglobal_Age_1519", package = "FPEMglobal")`.

FPEMglobal (*F*amily *P*lanning *E*stimation *M*odel global) implements a Bayesian hierarchical model for estimating and projecting the prevalence of contraceptive use and unmet need at the national level. This vignette concerns the application to adolescent women aged 15--19; for an introduction to the package see the vignette "FPEMglobal_Intro". 


# Accessing Default Input Data 

Default input data for adolescent women aged 15--19 can be accessed using the `system.file()` command. For example:

```{r access-default-inputs-1519, results="markup",echo=TRUE, eval = FALSE}
## Find the file path in the package file tree 
data_csv_filename_1519 <-
     system.file("extdata", "data_cp_model_all_women_15-19.csv", #NOTE: '15-19'
                 package = "FPEMglobal")

## Read in the file
data_df_1519 <-
     read.csv(data_csv_filename_1519, header = TRUE, as.is = TRUE)
   
```


# Estimates and Projections for Adolescent Women Aged 15--19

## Autopilot: All Adolescent Women Results

To implement estimation and projection for women aged 15--19 use the argument `age_group = "15-19"` in the functions `do_global_mcmc`, `do_global_run`, or `do_global_all_women_run`. The default, `age_group = "15-49"`, will produce estimates and projections for all women of reproductive age. 

Adjusted medians and special aggregates are handled in the same was as for the 15--49 age group via the arguments `adjust_medians` (default = `FALSE`) and `special_aggregates_name` (default = `NULL`), respectively. 

```{r autopilot-example-all-wom-global-1519,echo=TRUE,results="markup",cache=FALSE,eval = FALSE}

## Do a global run for women aged 15-19, including summarization. 

## Make sure you attach the package !!
library(FPEMglobal)

## Call the main function
all_women_runs_1519 <-
    do_global_all_women_run(
        ## Describe the run
        run_desc = "",
        age_group = "15-19", #....................................< SELECT '15-19' HERE
        data_csv_filename = "data_cp_model_all_women_15-19.csv", #< CHOOSE APPROPRIATE DATA
        ## MCMC parameters #......................................< CHANGE FOR FULL RUN!
        estimation_iterations = 2,
        burn_in_iterations = 1,
        steps_before_progress_report = 1,
        thinning = 1,
        chain_nums = 1:2,
        set_seed_chains = 1
    ) 
  
## See the run name !! 
## All women, married women, and unmarried women output
## folders have the same date-time in their names.
all_women_runs_1519

```


## Age-Ratio Family Planning Indicators

*FPEMglobal* can produce estimates and projections of the proportion of women of reproductive age using contraceptive methods, or experiencing unment need for contraception, that are aged 15--19. These are calculated as the ratio of in the respective family planning category aged 15--19 to the number in the category aged 15--49. The calculations are done at the trajectory level yielding true probabilistic estimates.

To compute age ratio indicators a completed model run for all women of reproductive age (i.e., age 15--49) must be available for each marital group desired. The output folder(s) of these runs are referred as `age_total` directories. Age ratios can be requested in `do_global_run` or `do_global_all_women_run` when starting a new run, or in `post_process` and `combine_runs` when adding to an existing run. The arguments all begin with `age_ratios_age_total_`. See the help files `?post_process_mcmc` and `?do_global_all_women_run` for an explanation in each case. 

`do_global_all_women_run` has an argument `age_ratios_age_total_run_name_prefix` to make it easier to select the 15--49 outputs if they follow the standard naming convention for runs explained in the vignette "FPEMglobal_Intro". All that need be supplied in that case is the common output folder name prefix. E.g., 
```
do_global_all_women_run(..., age_ratios_age_total_run_name_prefix = "200501_093015")
``` 
will look for the married women 15-49 outputs in "`r file.path("output", FPEMglobal:::make_run_name(marital_group = "married", age_group = "15-49", run_name_override = "200501_093015"))`"; unmarried and all women result output folder names will be constructed according to the same scheme. 

```{r autopilot-example-all-wom-global-1519-age-ratio,echo=TRUE,results="markup",cache=FALSE,eval = FALSE}

## Do a global run for women aged 15-19, including summarization, with age ratios 

# Call the main function
all_women_runs_1519 <-
    do_global_all_women_run(
        ## Describe the run
        run_desc = "",
        age_group = "15-19", #....................................< SELECT '15-19' HERE
        data_csv_filename = "data_cp_model_all_women_15-19.csv", #< CHOOSE APPROPRIATE DATA
        ## MCMC parameters #......................................< CHANGE FOR FULL RUN!
        estimation_iterations = 2,
        burn_in_iterations = 1,
        steps_before_progress_report = 1,
        thinning = 1,
        chain_nums = 1:2,
         set_seed_chains = 1,
        ## Age ratios
        age_ratios_age_total_run_name_prefix = "200501_093015" #..< COMMON PREFIX OF 15-49 OUTPUT FOLDERS
    ) 

```

The table below list the three methods by which the 15--49 results to be used for age ratio calculation can be selected, the functions they can be used with, and the corresponding function arguments.

+------------------------------+----------------------------------------+----------------------------------------------------------+
| Method                       | Function                               | Arguments                                                |
+==============================+========================================+==========================================================+
| Common prefix                | `do_global_all_women_run`              | `age_ratios_age_total_run_name_prefix`                   |
+------------------------------+----------------------------------------+----------------------------------------------------------+
| Run name                     | `do_global_run`                        | `age_ratios_age_total_run_name`                          |
+------------------------------+----------------------------------------+----------------------------------------------------------+
|                              | `do_global_all_women_run`              | `age_ratios_age_total_married_run_name`                  |
|                              |                                        | `age_ratios_age_total_unmarried_run_name`                |
|                              |                                        | `age_ratios_age_total_all_women_run_name`                |
+------------------------------+----------------------------------------+----------------------------------------------------------+
| Output folder path           | `do_global_run`                        | `age_ratios_age_total_output_folder_path`                |
+------------------------------+----------------------------------------+----------------------------------------------------------+
|                              | `do_global_all_women_run`              | `age_ratios_age_total_married_output_folder_path`        |
|                              |                                        | `age_ratios_age_total_unmarried_output_folder_path`      |
|                              |                                        | `age_ratios_age_total_all_women_output_folder_path`      |
+------------------------------+----------------------------------------+----------------------------------------------------------+


## Base Level Control

Base level control is available for adding results to, or reprocessing a completed model run. See the vignette "FPEMglobal_Intro" for details. The functions `post_process_mcmc`, `combine_runs`, and `make_results` do *not* take the `age_group` argument; this is read from the meta information saved by the `do_...` functions. 

In the following section, and an additional type of outputs is discussed: age ratios. The nature of this output is explained in that section. The table below gives a summary of the function call sequences needed to produce various combinations of outputs from a completed model run, including this two additional type. The completed run could have been obtained from any of the `do_...` functions. In the example calls, default values of arguments are assumed and are not explicitly specified. It is further assumed that the appropriate `run_name`s are passed as the first argument to all functions.

+-----------------------+-------------------------------------------------+---------------------------------------------------------------------------------+
| Marital Group         | Output                                          | Function call sequence                                                          |
+=======================+=================================================+=================================================================================+
| Married and unmarried | Age ratios, country level                       | `post_process_mcmc(..., age_ratios_age_total_output_folder_path = "NAME")` \    | 
|                       |                                                 | `make_results`                                                                  |
+-----------------------+-------------------------------------------------+---------------------------------------------------------------------------------+
|                       | Age ratios, std. aggregates                     | Age ratios, country level for *both* marital groups *and* all women completed \ |
|                       |                                                 | `make_results` (must run again)                                                 |
+-----------------------+-------------------------------------------------+---------------------------------------------------------------------------------+
|                       | Age ratios, spec. aggregates                    | Age ratios, country level for *both* marital groups *and* all women completed \ |
|                       |                                                 | `make_results(..., special_aggregates_name = "[name]")` (must run again)        |
+-----------------------+-------------------------------------------------+---------------------------------------------------------------------------------+
|                       | Adjusted median age ratios, country level       | Not available                                                                   |
+-----------------------+-------------------------------------------------+---------------------------------------------------------------------------------+
|                       | Adjusted median age ratios, std.aggregates      | Not available                                                                   |
+-----------------------+-------------------------------------------------+---------------------------------------------------------------------------------+
|                       | Adjusted median age ratios, spec. aggregates    | Not available                                                                   |
+-----------------------+-------------------------------------------------+---------------------------------------------------------------------------------+
| All women             | Age ratios, country level                       | `combine_runs(..., age_ratios_age_total_output_folder_path = "NAME")` \         |
|                       |                                                 | `make_results`                                                                  |
+-----------------------+-------------------------------------------------+---------------------------------------------------------------------------------+
|                       | Age ratios, std. aggregates                     | `combine_runs(..., age_ratios_age_total_output_folder_path = "NAME")` \         |
|                       |                                                 | `make_results`                                                                  |
+-----------------------+-------------------------------------------------+---------------------------------------------------------------------------------+
|                       | Age ratios, spec. aggregates                    | `combine_runs(..., age_ratios_age_total_output_folder_path = "NAME")` \         |
|                       |                                                 | `make_results(..., special_aggregates_name = "[name]")`                         |
+-----------------------+-------------------------------------------------+---------------------------------------------------------------------------------+
|                       | Adjusted median age ratios, country level       | Not available                                                                   |
+-----------------------+-------------------------------------------------+---------------------------------------------------------------------------------+
|                       | Adjusted median age ratios, std.aggregates      | Not available                                                                   |
+-----------------------+-------------------------------------------------+---------------------------------------------------------------------------------+
|                       | Adjusted median age ratios, spec. aggregates    | Not available                                                                   |
+-----------------------+-------------------------------------------------+---------------------------------------------------------------------------------+


# References {-}
